Evaluating an attempt to restore summer fire in the Northern Great Plains

### 2024-12-11 SpringSummerSeverity/paper/AllScriptTogetherSI.tex
draft SpringSummerSeverity

---
title: Evaluating an attempt to restore summer fire in the Northern Great Plains
author:
- Devan Allen McGranahan and Jay P. Angerer
subtitle:  'Supplementary Information'
header-includes:
  - \usepackage{amsmath}
  - \renewcommand{\familydefault}{\sfdefault}
  - \usepackage[colorlinks=true, citecolor=blue, urlcolor=blue,linkcolor=blue, pdfborder={0 0 0}]{hyperref}
  - \urlstyle{same}
  - \usepackage{xcolor} 
  - \usepackage{booktabs}
  - \raggedright
  - \usepackage{listings}
output:
  pdf_document:
    highlight: tango
    keep_tex: yes
    toc: false
---

@@

# Remote sensing

## Sentinel-2

This \texttt{EvalScript} can be used in the [Copernicus browser](https://browser.dataspace.copernicus.eu/) as a Custom script to create a Custom visualization that can be exported as a 16-bit \texttt{.tiff} for raster analysis. 
The user must select the area of interest and imagery dates and is responsible for assessing cloudiness.

@@

\clearpage
## Landsat

This script for [Google Earth Engine](https://code.earthengine.google.com/) exports a composited NDVI \texttt{.tiff} file to the user's Google Drive for the area of interest defined as \texttt{geometry} for an eight week period beginning with each date given in \texttt{listDate}. 
The script combines imagery from Landsat missions 5, 7, \& 8 and handles cloud masking.

@@

# Analysis

@@

## Remotely sensed imagery

@@

## Weather data

This script wrangles the weather data downloaded from the [North Dakota Ag Weather Network's Streeter station](https://ndawn.ndsu.nodak.edu/station-info.html?station=48).

@@

# Hourly data 
  WxData$HourlyWx <- 
    read_xlsx('./data/CGREC_weather.xlsx', 'hourly') %>%
    filter(between(Hour, 1000, 1700)) %>%
    unite( c(Year, Month, Day), col = 'date', sep = '-', remove = F) %>%
    unite( c(Month, Day), col = 'day', sep = '-', remove = F) %>%
    mutate(day = as.Date(day, '%m-%d'), 
           season = case_when(
             between(day, seasons$start[1], seasons$end[1]) ~'Spring', 
             between(day, seasons$start[2], seasons$end[2]) ~'Summer',
             TRUE ~ NA      
           ) ) %>%
    mutate(e = 6.11 * (10 ^ ( (7.5 * DewPoint)/ (237.3 + DewPoint) ) ), 
           es = 6.11 * (10 ^ ( (7.5 * AirTemp)/ (237.3 + AirTemp) ) ), 
           VPD = es - e) 
# Get burn day weather
  WxData$BurnDayWx <-
    HourlyWx  %>% 
    filter(date %in% BurnDays$date) %>%
    group_by(Year, date, season) %>%
    summarise_at(.vars = vars(c(DewPoint, RelHum, WindSpeed,VPD)),
                 .funs = c("mean")) %>%
    ungroup() %>%
    pivot_longer(names_to = 'variable', 
                 values_to = 'value', 
                 cols = DewPoint:VPD) %>%
    mutate(variable = recode(variable, 
                             'DewPoint' = 'Dew Point (°C)', 
                             'RelHum' = 'Relative Humidity (%)', 
                             'VPD' = 'Vapor Pressure Deficit', 
                             'WindSpeed' = 'Wind speed (m/s)') , 
           Year = as.character(Year)) 
\end{lstlisting}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{amsmath}
\renewcommand{\familydefault}{\sfdefault}
\usepackage[colorlinks=true, citecolor=blue, urlcolor=blue,linkcolor=blue, pdfborder={0 0 0}]{hyperref}
\urlstyle{same}
\usepackage{xcolor}
\usepackage{booktabs}
\raggedright
\usepackage{listings}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Evaluating an attempt to restore summer fire in the Northern Great Plains},
  pdfauthor={Devan Allen McGranahan and Jay P. Angerer},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Evaluating an attempt to restore summer fire in the Northern
Great Plains}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{Supplementary Information}
\author{Devan Allen McGranahan and Jay P. Angerer}
\date{}

\begin{document}
\maketitle

@@

\section{Remote sensing}\label{remote-sensing}

\subsection{Sentinel-2}\label{sentinel-2}

This \texttt{EvalScript} can be used in the
\href{https://browser.dataspace.copernicus.eu/}{Copernicus browser} as a
Custom script to create a Custom visualization that can be exported as a
16-bit \texttt{.tiff} for raster analysis. The user must select the area
of interest and imagery dates and is responsible for assessing
cloudiness.

@@

\clearpage

\subsection{Landsat}\label{landsat}

This script for \href{https://code.earthengine.google.com/}{Google Earth
Engine} exports a composited NDVI \texttt{.tiff} file to the user's
Google Drive for the area of interest defined as \texttt{geometry} for
an eight week period beginning with each date given in
\texttt{listDate}. The script combines imagery from Landsat missions 5,
7, \& 8 and handles cloud masking.

@@

\section{Analysis}\label{analysis}

@@

\subsection{Remotely sensed imagery}

The following \textsf{R} script processes the imagery produced by the scripts above after they have been saved to a drive that can be mapped to from the session as \texttt{imagery\_dir}.

@@

\newpage
\subsection{Weather data}\label{weather-data}

This script wrangles the weather data downloaded from the
\href{https://ndawn.ndsu.nodak.edu/station-info.html?station=48}{North
Dakota Ag Weather Network's Streeter station}.

@@

# Hourly data 
  WxData$HourlyWx <- 
    read_xlsx('./data/CGREC_weather.xlsx', 'hourly') %>%
    filter(between(Hour, 1000, 1700)) %>%
    unite( c(Year, Month, Day), col = 'date', sep = '-', remove = F) %>%
    unite( c(Month, Day), col = 'day', sep = '-', remove = F) %>%
    mutate(day = as.Date(day, '%m-%d'), 
           season = case_when(
             between(day, seasons$start[1], seasons$end[1]) ~'Spring', 
             between(day, seasons$start[2], seasons$end[2]) ~'Summer',
             TRUE ~ NA      
           ) ) %>%
    mutate(e = 6.11 * (10 ^ ( (7.5 * DewPoint)/ (237.3 + DewPoint) ) ), 
           es = 6.11 * (10 ^ ( (7.5 * AirTemp)/ (237.3 + AirTemp) ) ), 
           VPD = es - e) 
# Get burn day weather
  WxData$BurnDayWx <-
    HourlyWx  %>% 
    filter(date %in% BurnDays$date) %>%
    group_by(Year, date, season) %>%
    summarise_at(.vars = vars(c(DewPoint, RelHum, WindSpeed,VPD)),
                 .funs = c("mean")) %>%
    ungroup() %>%
    pivot_longer(names_to = 'variable', 
                 values_to = 'value', 
                 cols = DewPoint:VPD) 
\end{lstlisting}

\end{document}
